Tulai

### 2023-09-29 paper/paper.qmd
review chi-square test and PCA post-hoc

kable(
  summary_table_tool_area_percentage,
  col.names = c("Tools", "D1 (%)", "TA (%)", "TP1 (%)", "Total (%)"),
  caption = "Tool Typology in the three main areas (Percentage)"
)

@@

biplot_modified <- 
ggbiplot(
  pca_data.pca,
  obs.scale = 1,
  var.scale = 1,
  groups = excavation_area,
  ellipse = FALSE,
  circle = TRUE) +
  stat_chull(aes(color = excavation_area,
                 fill = excavation_area),
             alpha = 0.1,
             geom = "polygon") +
  scale_colour_brewer(palette = "Set1",
                      name = '',
                      guide = 'none') +
  scale_fill_brewer(palette = "Set1",
                    name = '')  +
  theme_minimal()

@@

ggsave(here::here("figures/fig-pca-biplot.jpg"),
       h = 6, 
       w = 8)

>>>>

@@

library(ggpubr)
library(ggbiplot)

pca_data.pca <- prcomp(pca_data, scale. = TRUE)

biplot_modified <- 
ggbiplot(
  pca_data.pca,
  obs.scale = 1,
  var.scale = 1,
  groups = excavation_area,
  ellipse = FALSE,
) +
  stat_chull(aes(color = excavation_area,
                 fill = excavation_area),
             alpha = 0.1,
             geom = "polygon") +
  scale_colour_brewer(palette = "Set1",
                      name = '',
                      guide = 'none') +
  scale_fill_brewer(palette = "Set1",
                    name = '')  +
  theme_minimal()

@@

ggsave(plot = biplot_modified,
       filename = here::here("figures/fig-pca-biplot.jpg"),
       h = 6, 
       w = 8)
